Bacterial Microbiome and Obesity Meta-analysis Sequence Processing Pipeline

### 2016-03-30 code/sequenceProcessing.Rmd
minor sequence processing update

---
title: "Bacterial Microbiome and Obesity Meta-analysis Sequence Processing Pipeline"
author: "Marc Sze"
date: "January 26, 2016"
output: 
  html_document:
    keep_md: yes
bibliography: ../metaAnalysis.obesity.microbiome.bib
---
#### **Preamble**  
Each study is brought up one at a time.  This recount starts from time of download all the way to generation of the final shared file used for the meta-analysis in the study.  You will also need the latest version of mothur, SRA Toolkit, and Python 3+ installed on your system.  There are also a few reference files that you will need.  The first is the [SILVA reference](http://www.mothur.org/wiki/Silva_reference_files) database and the second is the [RDP database](http://www.mothur.org/wiki/RDP_reference_files) of which we used release 102 and version 9 respectively.  In general, we tried to keep as close as possible to the Schloss SOP for processsing sequence reads for either 454 or the MiSeq.  Most of the differences between the SOP as written and what was performed involved the use of flowgrams.  Most of the data in the SRA were stored in the Fastq format and this step was not possible.  The batch files can be found in the data/process directory under the respective study directory.
<br>
<br>

>>>>

---
title: "Bacterial Microbiome and Obesity Meta-analysis Sequence Processing Pipeline"
author: "Marc Sze"
date: "January 26, 2016"
output: 
  html_document:
    keep_md: yes
bibliography: ../metaAnalysis.obesity.microbiome.bib
---
#### **Preamble**  
Each study is brought up one at a time.  This recount starts from time of download all the way to generation of the final shared file used for the meta-analysis in the study.  You will also need the latest version of mothur, SRA Toolkit, and Python 3+ installed on your system.  There are also a few reference files that you will need.  The first is the [SILVA reference](http://www.mothur.org/wiki/Silva_reference_files) database and the second is the [RDP database](http://www.mothur.org/wiki/RDP_reference_files) of which we used release 102 and version 9 respectively.  In general, we tried to keep as close as possible to the Schloss SOP for processsing sequence reads for either 454 or the MiSeq.  Most of the differences between the SOP as written and what was performed involved the use of flowgrams.  Most of the data in the SRA were stored in the Fastq format and this step was not possible.  The batch files can be found in the data/process directory under the respective study directory.  Our specific server used a PBS script for job submission and an example of it can be found below.  If you want to copy it simply save it as a .pbs file.

```{r, engine='bash', eval=FALSE}
#!/bin/sh
#PBS -l nodes=1:ppn=8,mem=44gb
#PBS -l walltime=500:00:00
#PBS -j oe
#PBS -m abe
#PBS -V
#PBS -M email@location.com
#PBS -q first

echo "ncpus-2.pbs"
cat $PBS_NODEFILE
qstat -f $PBS_JOBID

cd $PBS_O_WORKDIR

NCPUS=`wc -l $PBS_NODEFILE | awk '{print $1}'`

/mnt/EXT/Schloss-data/bin/mothur Turnbaugh1.batch

echo "qsub working directory absolute is"
echo $PBS_O_WORKDIR
exit 0

<br>
<br>
